Simulating an Isolated Dwarf Galaxy with Multi-Channel Feedback and Chemical Yields from Individual Stars

### 2018-08-20 main.tex
bugfix
Adding text about G_o UVB value for Figure 7. changing Figure to Fig. (and Figures to Figs.)

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution. This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds. This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively. Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels. The ISM properties are quantified further in Section~\ref{sec:phase}.

@@

Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}. In the final column of Figure~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc. With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view. At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$. These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Figure~\ref{fig:panel_x}, but showing face-on views.}
\label{fig:panel_z}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
\label{fig:scale_height}
\end{figure}

@@

We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Figure~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr. The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Figure~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%. The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback. For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr. The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds. During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

@@

Figure~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr. One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Figure~\ref{fig:ISM_evolution}. The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component. The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run. The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation. During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1. Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated. However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}.

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The contribution from the metagalactic background falls below the lower vertical axis limit on this plot. The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions. At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity.}
\label{fig:ISRF}
\end{figure}

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Figure~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Figure~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It remains to be seen which of these two modes of feedback is more important in regulating star formation.

@@

The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}. However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}. In Figure~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
\begin{equation} \label{eq:dotM}
\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
\end{equation} 
We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Figure~\ref{fig:mass_outflow}. Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor. For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time. This declines towards larger radii, however, with substantially less outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results. The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.

@@

Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations. In Figure~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases. Gas with a negative velocity is moving towards the center of the halo. Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo. Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$. Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$. The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$. The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}. However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass. Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM. Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however. The amount of transfer between phases in the halo of our galaxy will be investigated in future work.

\begin{figure}
\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. This is averaged over the same time interval as Figure~\ref{fig:ISRF}. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM.}
\label{fig:outflow_velocity}
\end{figure}

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. These metal loading factors fluctuate significantly with the SFR, just as was shown in Figure~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5. On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5). Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_retention}
\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Figure~\ref{fig:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

@@

For our simulated dwarf galaxy, we find:
\begin{enumerate}
\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies. (See Figures~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).

>>>>

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}. These figures show inside-out star formation, as star formation propagates from the inner regions outward during the galaxy's evolution. This is clear in the face-on panels, which demonstrate the growth of the stellar population from the center outward, and the declining gas densities inside-out as a result of stellar feedback driven winds. This central region quickly fills with warm and hot gas generated from radiation feedback and SNe respectively. Both the ISM and the halo gas are multi-phase, containing gas at cold, warm, and hot temperatures with a range of densities, as evident in the temperature slices in both panels. The ISM properties are quantified further in Section~\ref{sec:phase}.

@@

Constraining the gas scale height in ultra-faint dwarf galaxies observationally is challenging. For Leo P, located at 1.7~Mpc, HI observations that are capable of detecting the diffuse HI throughout the galaxy have a resolution of 100--200 pc, with higher resolution observations identifying only the densest HI clumps in the galaxy \citep[e.g.][]{Bernstein-Cooper2014}. In the final column of Fig.~\ref{fig:panel_z}, the peak HI column density reaches $N_{\rm HI} = 9.4 \times 10^{21}$~cm$^{-2}$, but is located in dense regions with sizes $<$ 10$\sim$pc. With a resolution of 100~pc, the peak column density in an edge-on view is $N_{\rm HI} = 4.3 \times 10^{20}$~cm$^{-2}$, and $N_{\rm HI} = 2.8 \times 10^{20}$~cm$^{-2}$ in a face-on view. At 500 pc resolution, this corresponds to $N_{\rm HI} = 7.5 \times 10^{19}$~cm$^{-2}$, and $N_{\rm HI} = 6.2 \times 10^{19}$~cm$^{-2}$. These column densities are consistent with the resolution-dependent peak column densities found in the low mass dwarf galaxy sample of \cite{Teich2016}, and consistent with the observed peak column density of Leo P, $N_{\rm HI} = 6.5 \times 10^{20}$~cm$^{-2}$, observed with a spatial resolution of about 33~pc.

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_z.png}
\caption{Same as Fig.~\ref{fig:panel_x}, but showing face-on views.}
\label{fig:panel_z}
\end{figure*}

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figs.~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
\label{fig:scale_height}
\end{figure}

@@

We present the star formation rate (SFR) and core collapse SN rate (SNR) evolution of our dwarf galaxy as measured in 10 Myr bins in the left panel of Fig.~\ref{fig:sfr_mass_evolution}.\footnote{We do not show the Type Ia rate as there have only been 16 by the end of the simulation.} Within the first 50 Myr of evolution the SFR rises quickly to nearly $10^{-3}$ M$_{\odot}$ yr$^{-1}$, declining to $\sim 3 \times 10^{-4}$~M$_{\odot}$~yr$^{-1}$ until a significant drop off at about 130 Myr. The remainder of the evolution is characterized by periods of little to no star formation interspersed with periods of continual, but low star formation around $10^{4}$~M$_{\odot}$~yr$^{-1}$. The SNR tracks the SFR with a time delay, with roughly one core collapse SNe per 100 M$_{\odot}$ of star formation. Averaging over the entire simulation time, we obtain  $<\rm{SFR}> = 1.19 \times 10^{-4}$ M$_{\odot}$ yr$^{-1}$. We discuss how the SFR of this galaxy compares to observed galaxies in Section~\ref{sec:observation}.

@@

At initialization, all H and He of our dwarf galaxy is neutral, with no molecular hydrogen component. By the time of first star formation ($t=0$ in Fig.~\ref{fig:sfr_mass_evolution}), HI still dominates the mass of the galaxy, with a molecular hydrogen mass fraction of only $\sim$~0.3~\%. The molecular component declines rapidly as this gas is both converted into stars and is destroyed by stellar radiation feedback. For the remainder of the simulation, the H$_2$ mass generally increases,  with small fluctuations during periods of star formation, reaching a peak mass fraction of 5\% at 500~Myr. The growth of the molecular fraction is due in part to a decline in the total gas content of our galaxy from feedback-driven galactic winds. During these outflows, the densest gas, the molecular gas, is preferentially retained over the more diffuse ISM. Examining the molecular properties of the ISM in low mass dwarf galaxies in more detail is a vital avenue of future research, as there are significant observational uncertainties in deriving H$_2$ content of galaxies in this low metallicity regime \citep{Leroy2008,McQuinn2012,Amorin2016}. The molecular properties of our galaxy are discussed further in context with other works in Section~\ref{sec:observation}.

@@

Fig.~\ref{fig:phase} shows the temperature-density distribution of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300--350~Myr. One can readily identify the two regimes containing most of the mass in the simulation: low density, warm gas produced through ionization and SN heating, and cold, high density gas that makes up most of the mass in the galaxy's disk (see Fig.~\ref{fig:ISM_evolution}). Several notable features of the distribution include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well-defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. Our artificial temperature ceiling in diffuse gas (see Section~\ref{sec:hydro}) is seen clearly by the horizontal feature in the top left. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does appear in this time average.

@@

The mass of the ISM in our dwarf galaxy is dominated by the CNM for the entirety of the simulation, as shown in the left panel of Fig.~\ref{fig:ISM_evolution}. The mass fraction of the remaining phases are ordered by temperature, with the WNM as the next most-significant component. The WNM is initially comparable to the CNM, but comprises a mass fraction of about 0.1 by the end of the run. The WIM and HIM fluctuate significantly, corresponding to fluctuations in the SFR and associated feedback, but are subdominant throughout the simulation. During periods of peak stellar feedback, however, the WIM can reach a mass fraction above 0.1. Although the CNM dominates the mass fraction, it is a negligible component of the ISM volume, which is WIM dominated. However, the large, anti-correlated fluctuations in the WNM and HIM make these three phases often comparable. Together, these figures better quantify the general properties observed in the panel plots in Fig.~\ref{fig:panel_x} and Fig.~\ref{fig:panel_z}.

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Fig.~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 100 Myr during the period of star formation from roughly 250--350~Myr. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The averaged profile varies between values of 0.02 and 0.1, with peaks located at radii of the few active star formation regions. At any given radius, there is over a two order magnitude variation in the ISRF during this period of time.

@@

\begin{figure}
\includegraphics[width=0.95\linewidth]{G_o_profile} \\
\includegraphics[width=0.95\linewidth]{ionizing_photon_profile}
\caption{
Azimuthally averaged radial profiles of the ISRF in the mid-plane of our galaxy in two different bands, time-averaged over 50 Myr from 300 -- 350~Myr. Here we define the midplane as within 2.5~$dx$ of z = 0, or 4.5~pc. The top panel gives $G_{\rm o}$, the flux of radiation between 6--13.6 eV normalized to the value in the solar neighborhood, shaded between minimum and maximum values at each position, with the average shown as a black line. The bottom panel gives the HI ionizing stellar radiation flux. Since this radiation is tracked directly through radiative transfer, the minimum value at all radii is 0 at some point. For this reason we only shade between the first quartile and maximum values. HeI ionizing radiation is very similar to HI ionizing radiation, with a small vertical offset, and is not shown for clarity. In the top panel, the minimum of the vertical axis is the UVB value of $G_o$.}
\label{fig:ISRF}
\end{figure}

\begin{figure*}
%\centering
\includegraphics[width=0.45\linewidth]{g_o_2D_phase}
\includegraphics[width=0.45\linewidth]{q_o_2D_phase}
\caption{Single-snapshot 2D radial profile plots at 300~Myr of the ISRF in two flux bands, $G_{\rm o}$ and HI ionizing radiation, illustrating the full dynamic range of radiation flux at a given radius in the galaxy. Here, we include all gas within the mid-plane of our dwarf galaxy. Since a majority of the mass of the galaxy is in the cold phase (see Fig.~\ref{fig:phase}), and is therefore optically thick to HI ionizing radiation, it does not show up in the HI ionizing radiation diagram. This gas readily appears in the $G_{\rm o}$ diagram since we assume it to be optically thin, though we do apply a localized shielding approximation.}
\label{fig:ISRF_2D}
\end{figure*}

To further quantify the local variations in these radiation fields, we present the full distribution of $G_{\rm o}$ and the HI ionizing flux in Fig.~\ref{fig:ISRF_2D} at a single snapshot at 300~Myr. This diagram shows how dramatic the increase in ISRF near young, massive stars is (the spikes in both diagrams), while much of the mid-plane sees an ISRF orders of magnitude lower. The striking contrast between the two diagrams is due to the shielding of the HI ionizing flux in the most massive (cold and dense) regions of the galaxy through the radiative transfer calculations; shielding of the FUV radiation is approximate and in general weaker, making these regions more prominent in the left hand figure (the pink/white clumps). From both of these diagrams, it is clear that the ISRF of a low mass dwarf galaxy varies greatly over time and space in a way that cannot be appropriately captured by an analytic profile. Although one could adopt an averaged radial profile to provide a realistic, global source of energy for thermal pressure support of the gas against collapse, it is unclear how sufficient this would be in suppressing star formation. In particular, the large increases around sites of recent star formation could be important sources of feedback to destroy molecular clouds and reduce their effective star formation efficiency. It remains to be seen which of these two modes of feedback is more important in regulating star formation.

@@

The recent FIRE cosmological simulations of dwarf galaxies over a range of dark matter halo masses find that they exhibit large outflows, with mass loading factors ($\eta = \dot{M}_{\rm out}/<\rm{SFR}>$) on order of 100--1000 \citep{Muratov2015}. However, comparable models of idealized dwarf galaxies with detailed feedback and physics treatments find more modest mass loading factors \citep{Hu2016,Hu2017}. In Fig.~\ref{fig:mass_outflow} we present the mass outflow and mass loading rates for our dwarf galaxy as a function of time, computed at five different positions from the galaxy. We follow \citet{Muratov2015} in defining the mass outflow rate at any given radius to be the sum of the outflow rate in all cells in a spherical annulus of width $dL$ centered at that radius,
\begin{equation} \label{eq:dotM}
\dot{M}_{\rm out} = \sum M_{\rm gas} \times v_{\rm r} / dL.
\end{equation} 
We choose $dL = 0.1~R_{\rm vir}$, or 2.74 kpc.

The total mass outflow rates and mass loading factors at 0.1, 0.25, 0.5, and 1.0 $R_{\rm vir}$ are shown in Fig.~\ref{fig:mass_outflow}. Generally, other works use gigayear timescale measurements of the SFR to compute the mass loading factor. For consistency with those works, we use the 500~Myr average SFR for computing the mass loading factor. The outflow rate at 0.1 $R_{\rm vir}$ is high, corresponding to mass loading factors between 20--100 throughout the simulation time. This declines towards larger radii, however, with substantially less outflow past the virial radius. \citet{Muratov2015} finds typical mass loading factors at 0.25 R$_{\rm vir}$ on order of 20--40 for galaxies with $v_{c} = 30$ km s$^{-1}$ at low redshift, consistent with our results. The fluctuations in both of these panels are directly correlated with the SFR, with increased outflow during periods of star formation, and decreased outflow during periods of quiescence.

@@

Detailed outflow properties, beyond outflow rates and mass loading factors, can help discriminate between the model dependent feedback physics included in galaxy simulations. In Fig.~\ref{fig:outflow_velocity} we present radial velocity distributions of all material outside our dwarf galaxy's disk, and within the halo, broken into three gas phases. Gas with a negative velocity is moving towards the center of the halo. Roughly 25\% of this mass is inflowing, mostly with modest negative velocities, and corresponds to previously ejected gas mixing and recycling throughout the halo. Half of the outflowing gas (positive velocities) is moving at velocities below 30 km s$^{-1}$, 75\% at velocities below 70 km s$^{-1}$, and 95\% at velocities below 100 km s$^{-1}$. Although the mass contained in the tails of these distributions is a sub-dominant fraction of the total, there is still a non-negligible amount of gas moving at velocities of a few hundreds of km/s, with a peak velocity of over 700 km s$^{-1}$. The WNM and WIM together dominate the mass of both the inflowing and outflowing gas, with the WIM and HIM dominating at velocities above 200 km s$^{-1}$. The dominant launching mechanism in this simulation is SN feedback, which generates a rapidly moving and volume-filling WIM and HIM, consistent with the results in \citet{Hu2016,Hu2017}. However, as shown, the HIM, which is mostly the SN ejecta itself, comprises very little of the outflow by mass. Most of the outflowing gas (by mass) comes from the warm phase, pushed out by the high pressure, fast moving HIM. Some of this warm gas certainly originates from adiabatically and radiatively cooled HIM, however. The amount of transfer between phases in the halo of our galaxy will be investigated in future work.

\begin{figure}
\includegraphics[width=0.95\linewidth]{velocity_distribution_time_average}
\caption{The time averaged radial velocity distribution of outflowing material external to the disk and within the virial radius of our dwarf galaxy. This is averaged over the same time interval as Fig.~\ref{fig:ISRF}. The outflowing material is multiphase, broken into WNM, WIM, and HIM. See Section~\ref{sec:phase} for definitions of these regimes. We note that WNM is often labeled simply as ``cold'', or gas below $T = 10^{4}$~K. There is little to no outflowing mass in the CNM.}
\label{fig:outflow_velocity}
\end{figure}

@@

\subsubsection{Metal Enriched Outflows}
Dwarf galaxies efficiently, and preferentially, eject metals released in stellar feedback from their shallow potential wells \citep{MacLowFerrara1999,FerraraTolstoy2000}. This has been better quantified recently both observationally \citep[e.g.][]{Kirby2011-metals,Zahid2012,Peeples2014,McQuinn2015} and with more detailed cosmological simulations \citep{Simpson2013,Angles-Alcazar2017,Muratov2017}. In the top panel of Fig.~\ref{fig:metal_evolution}, we give the metal mass loading factor for our galaxy over time, at the same radii as in Fig.~\ref{fig:mass_outflow}. The parameter used to quantify metal outflow efficiencies varies among works. Here, we define the metal mass loading factor as the metal outflow rate divided by the metal production rate, or
\begin{equation} \label{eq:eta-metal}
\eta_{\rm metal} = \frac{\dot{M}_{\rm metal}}{\rm{SFR} \times (M_{\rm metal}/M_{*})},
\end{equation}
where $\dot{M}_{\rm metal}$ is the metal mass outflow rate, $M_{\rm metal}$ is the total mass in metals produced, and $M_{*}$ is the total mass in stars. These metal loading factors fluctuate significantly with the SFR, just as was shown in Fig.~\ref{fig:mass_outflow}, reaching a minimum of about 0.05, but peaking at around 5. On average, over the simulation time, $\eta_{\rm metal}$ is below unity (around 0.5). Recent simulations of outflows from a Milky Way type disk indicate typical $\eta_{\rm metal}$ comparable to our results, usually between 0.5 and 1 \citep{Li2017,Fielding2017}. \cite{Muratov2017} computes a slightly different quantity for their galaxies, the normalized metal outflow rate $\eta_{Z} = \dot{M}_{\rm metal}/{\rm SFR}$, finding values of about 0.02 at 0.25~$R_{\rm vir}$ regardless of galaxy circular velocity. Our galaxy is consistent with this value, with an average $\eta_Z = 0.015$, fluctuating between 0.007 and 0.02.

\begin{figure}
\includegraphics[width=0.9\linewidth]{metal_mass_loading} \\
\includegraphics[width=0.9\linewidth]{metal_retention}
\caption{{\bf Top}: Metal mass loading factor (see Eq.[~\ref{eq:eta-metal}]) at the same radii as in Fig.~\ref{fig:mass_outflow}. This is the ratio between the metal outflow rate and the metal production rate. {\bf Bottom}: The fraction of metals contained in the disk, CGM, and outside the halo of our dwarf galaxy over time. In both panels, we consider the total mass of all individually tracked metal species, which is zero at initialization, not the aggregate total metallicity field, which is non-zero at initialization.}
\label{fig:metal_evolution}
\end{figure}

@@

For our simulated dwarf galaxy, we find:
\begin{enumerate}
\item Multi-channel feedback is effective in regulating star formation to a rate consistent with the Kennicutt-Schmidt relationship and the extended Schmidt law in observed galaxies. (See Figs.~\ref{fig:sfr_mass_evolution} and \ref{fig:KS}).

\item This feedback drives large outflows having mass loading factors of $\eta \sim 50$ at 0.25~R$_{\rm vir}$, falling to $\eta \sim 10$ at R$_{\rm vir}$,  and
metal mass loading factors near unity. By mass, nearly all of this outflow is moving with velocities below 100~km~s$^{-1}$, but there is a significant tail towards velocities up to 1000~km~s$^{-1}$ (See Fig.~\ref{fig:outflow_velocity}).
